Analysis and elimination of bottlenecks\\ in parallel algorithm for solving\\ global optimization problems

### 2022-04-15 2022/RSD/paper.tex
after submission

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The paper presents the results of investigation of efficiency of the parallelization of a global optimum search algorithm. Two stages of solving the problem were distinguished: the search of a rough approximation to the global solution and its local refining. The novelty of the parallel algorithm considered in the present pa-per consists in the parallelization of the whole computational process -- both at the global search stage and at the one of the local refining of the solution found. The theoretical estimates of the algorithm parallelization efficiency are presented. The computational experiments were carried out. The results of the ones confirmed the theoretical conclusions.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}

@@

The main requirement to forming the corrections $U^k$ of particular form is the secant equation $B^{k+1} (y^{k+1} - y^k )= \nabla \varphi(y^{k+1})- \nabla \varphi(y^k)$, which is performed for all quasi-Newton methods. For more precise determination of the matrix $B^{k+1}$, it is necessary to impose additional requirements on the Hessian approximation. The set of such requirements is determined by BFGS rule. Assume
\begin{gather}
s_k = y^{k+1} - y^k, \nonumber \\
z^k = \nabla \varphi(y^{k+1})- \nabla \varphi(y^k). \nonumber
\end{gather}

>>>>

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The paper presents the results of investigation of efficiency of the parallelization of a global optimum search algorithm. Two stages of solving the problem were distinguished: the search of a rough approximation to the global solution and its local refining. The novelty of the parallel algorithm considered in the present paper consists in the parallelization of the whole computational process, both at the global search stage and at the one of the local refining of the solution found. The theoretical estimates of the algorithm parallelization efficiency are presented. The computational experiments were carried out. The results of the ones confirmed the theoretical conclusions.

\keywords{Multiextremal functions \and Lipschitz condition \and Global optimization \and Local optimization \and Parallel algorithms}
\end{abstract}
%
%
%
\section{Introduction}

@@

The main requirement to forming the corrections $U^k$ of particular form is the condition
$$B^{k+1} (y^{k+1} - y^k )= \nabla \varphi(y^{k+1})- \nabla \varphi(y^k),$$
that holds true for all quasi-Newton methods. For more precise determination of the matrix $B^{k+1}$, it is necessary to impose additional requirements on the Hessian approximation. The set of such requirements is determined by BFGS rule. Assume
\begin{gather}
s_k = y^{k+1} - y^k, \nonumber \\
z^k = \nabla \varphi(y^{k+1})- \nabla \varphi(y^k). \nonumber
\end{gather}
